The Effect of Elections and Prime Ministers on Discussion in the Australian Federal Parliament (1901--2018)

### 2018-12-15 outputs/docs/events/paper.Rmd
Add economics examples

**[Insert the econ examples. Zoom in on the Great Depression, the Premiers' Plan, the 80s/90s, privatisation debate.]**

>>>>

In Figure \@ref(fig:greatd) we focus on the period around the Great Depression and the Premiers' Plan.

```{r greatd, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes around the the Great Depression", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example-GreatD.pdf")
```

In Figure \@ref(fig:theeightsnighties) we focus on the period of the 1980s and 1990s when there was a great deal of economic change.

```{r theeightsnighties, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes during the 1980s and 1990s", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example-the80s.pdf")
```

In Figure \@ref(fig:economicsgfc) we focus on the financial crisis of 2007-08.

```{r economicsgfc, cache = TRUE, echo = FALSE, fig.cap = "Economic topic changes around the 2007-08 financial crisis", out.width = '100%'}
knitr::include_graphics("../../figures/topics_example-GFC.pdf")
```
